---
title: "Animation with SMIL"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Animation with SMIL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "  "
)
```

```{r setup}
library(minisvg)
```


Introduction
==============================================================================

There are at least 5 methods of animating SVG. These methods are detailed on the [w3.org pages](https://www.w3.org/TR/SVG/animate.html)).

The 5 methods are as follows:

1. SMIL - Synchronized Multimedia Integration Language.  [MDN doc](https://developer.mozilla.org/en-US/docs/Web/SVG/SVG_animation_with_SMIL)
2. CSS Animations [w3 css animation reference](https://www.w3.org/TR/css-animations-1/)
3. CSS Transitions [w3 css transitions reference](https://www.w3.org/TR/css-transitions-1/)
4. SVG DOM manipulation via scripting  [w3 reference](https://www.w3.org/TR/SVG/types.html#SVGDOMOverview)
5. Web Animation [w3 web animation reference](https://www.w3.org/TR/web-animations-1/)

This vignette assumes you are familiar with SVG tags and document structures.

This document describes method 1 - SMIL animation


SMIL animation
==============================================================================

SMIL stands for [Synchronized Multimedia Integration Language](http://www.w3.org/TR/REC-smil).

The way it works is to add an `animate`, `animateTransform` or `animateMotion` tag
as a child of the element to be animated.

The `animate` tag describes the parent attribute to be modified 
and a list of states for that attribute, or perhaps a path to be followed.

The following examples are adaptions of the [MDN docs on SMIL animation](https://developer.mozilla.org/en-US/docs/Web/SVG/SVG_animation_with_SMIL)


The `animate` tag
==============================================================================

Use `animate` with `from` and `to`
------------------------------------------------------------------------------

An easy way to use `animate` is to just specify the start and end values of an 
attribute.  

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build a small SVG with a circle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc(width = 240, height = 100)
doc$title("Attribute animation with SMIL")
doc$rect(x=0, y=0, width=240, height = 100, stroke='black', fill='white', stroke_width = 1)
circle <- doc$circle(cx = 20, cy = 50, r=15, fill = 'blue', stroke = 'none', stroke_width = 1)
```


<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```



```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add an 'animate' child to the circle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
circle$animate(attributeName = 'cx', from=-20, to=260, dur=5, repeatCount = 'indefinite')
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```




Use `animate` with `keyTimes`
------------------------------------------------------------------------------

To have more control of the animation over time, you can set a particular value
(`values`) at a set of nominated key frames (`keyTimes`)

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build a small SVG with a circle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc(width = 240, height = 100)
doc$title("Attribute animation with SMIL")
doc$rect(x=0, y=0, width=240, height = 100, stroke='black', fill='white', stroke_width = 1)
circle <- doc$circle(cx = 20, cy = 50, r=15, fill = 'blue', stroke = 'none')

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Animate the X coordinate of the circle giving it key times and 
# corresponding values
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
circle$animate(
  attributeName = 'cx', 
  keyTimes     = c( 0, 0.25, 0.5, 0.75,  1), 
  values       = c(20  , 60, 220,   60, 20),
  dur          = 5, 
  repeatCount = 'indefinite'
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Also animate the y coordinate
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
circle$animate(
  attributeName = 'cy', 
  keyTimes     = c( 0, 0.33, 0.66, 0.9,  1), 
  values       = c(50,  100,   50,   0, 50),
  dur          = 5, 
  repeatCount = 'indefinite'
)
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```



The `animateTransform` tag
==============================================================================

As the name suggests `animateTransform` lets you animate the transformation associated
with its parent.  We are no longer animating a simple attribute but the entire transformation
which puts the object into the document.


```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build a small SVG with a rectangle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc(width = 240, height = 100)
doc$title("Attribute animation with SMIL")
doc$rect(x=0, y=0, width=240, height = 100, stroke='black', fill='white', stroke_width = 1)
rect <- doc$rect(x=80, y=40, width=15, height=34, fill = 'blue', stroke = 'none')

rect$animateTransform(
  attributeName = 'transform',
  type          = 'rotate',
  from          = c(0  , 120, 50),
  to            = c(360, 120, 50),
  dur           = 5,
  repeatCount   = 'indefinite'
)
```




<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```



The `animateMotion` tag
==============================================================================

`animateMotion` is a way of animating the position and rotation of an element by
moving it along a path.


```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build a small SVG with a circle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc(width = 300, height = 100)
doc$title("Attribute animation with SMIL")
doc$rect(x=0, y=0, width=300, height = 100, stroke='black', fill='white', stroke_width = 1)
rect <- doc$rect(x=0, y=0, width=20, height=20, fill = 'blue', stroke = 'none')

rect$animateMotion(
  path = "M 250,80 H 50 Q 30,80 30,50 Q 30,20 50,20 H 250 Q 280,20,280,50 Q 280,80,250,80Z",
  dur         = 3,
  repeatCount = 'indefinite',
  rotate      = 'auto'
)
```


<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```
