---
title: "Animation with CSS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Animation with CSS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "  "
)
```

```{r setup}
library(minisvg)
```


Introduction
==============================================================================

There are at least 5 methods of animating SVG. These methods are detailed on the [w3.org pages](https://www.w3.org/TR/SVG/animate.html)).

The 5 methods are as follows:

1. SMIL - Synchronized Multimedia Integration Language.  [MDN doc](https://developer.mozilla.org/en-US/docs/Web/SVG/SVG_animation_with_SMIL)
2. CSS Animations [w3 css animation reference](https://www.w3.org/TR/css-animations-1/)
3. CSS Transitions [w3 css transitions reference](https://www.w3.org/TR/css-transitions-1/)
4. SVG DOM manipulation via scripting  [w3 reference](https://www.w3.org/TR/SVG/types.html#SVGDOMOverview)
5. Web Animation [w3 web animation reference](https://www.w3.org/TR/web-animations-1/)

This vignette assumes you are familiar with SVG tags and document structures.

This document describes method 2 - CSS animation.


CSS animation
==============================================================================

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build a small SVG with a rectangle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc(width = 240, height = 100)
doc$title("Attribute animation with SMIL")
doc$rect(x=0, y=0, width=240, height = 100, stroke='black', fill='white', stroke_width = 1)
doc$rect(id = 'myrect', x = 80, y=20, width=80, height=60)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Add a CSS style block to the SVG document. CSS definitions will override
# any inline definitions defined above
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc$defs("<style type='text/css'><![CDATA[
      @keyframes moveit {
        from { fill: green; }
        50%  { fill: blue; }
        to   { fill: yellow; }
      }
      
      #myrect {
        fill: green;
        animation-name: moveit;
        animation-duration: 5s;
        animation-iteration-count: infinite;
      }
    ]]>
    </style>")

```


<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```