---
title: "editing-svgs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{editing-svgs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "  "
)
```

```{r setup, message=FALSE}
library(minisvg)
library(purrr)
```

# Manipulating/Editing an Existing SVG

Editing SVG can be tricky because they are nested structures.

`{minisvg}` contains *some* tools for interogating/manipulating existing SVG, but 
the current focus in {minisvg} is really **creating** SVG documents in R.


# Overview of the structure of a {minisvg} document

A {minisvg} SVG document is just a tree of R6 objects, where each object represents
a single SVG tag (e.g. `<rect>` or `<pattern>`).  


Each object has a list of children (`$childen`) and
a list of attributes (`$attrib`).

There is also an alternate representation of the child elements of a node in the 
member `$child`. E.g. All the children of the current element which are `<rect>` tags
are stored in the list `$child$rect`

# Example SVG for this vignette

```{r}
svg_text <- '
<svg width="400" height="400" viewBox="0 0 400 400" xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink">
  <g>
    <circle fill="lightgrey" cx="50%" cy="50%" r = "45%" id="bgcircle" stroke="black" stroke-width="4" />
  </g>
  <rect fill="red"    x="40%" y="10%" width="20%" height="20%" />
  <rect fill="yellow" x="40%" y="40%" width="20%" height="20%" />
  <g>
    <rect fill="green"  x="40%" y="70%" width="20%" height="20%" id="gogogo" stroke="black" stroke-width="4" />
  </g>
</svg>'

doc_orig <- minisvg::parse_svg_doc(svg_text)
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc_orig)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc_orig$show()
} else {
  doc_orig
}
```


# Selecting and editing an element by its index in `$children`

If the structure of an SVG document is known, the element may be selected by its 
index in the `$children` list of all child nodes.

In this example, the second child of the root document is selected (i.e. the red square) and its 
fill attribute is updated.

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Extract the first rectangle and change its fill attribute
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc         <- doc_orig$copy()
first_child <- doc$children[[2]]

first_child$attribs$fill <- 'pink'
```



<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```


# Selecting and editing all direct child elements by type

Each SVG element node keeps both a `$children` list of nodes (which is arranged by 
insertion order), and a `$child` list which is grouped by tag names.

All direct child elements with a particular tag name, e.g. `circle`, may be accessed using
`$child[['circle']]`.

In the following example, the **two** direct child rectangles have their `fill` attribute updated.
Note that the small green rectangle is not updated as it is not a direct child of the root document.



```{r}
doc   <- doc_orig$copy()
rects <- doc$child$rect

purrr::walk(rects, ~.x$update(fill = 'blue'))
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```


# Selecting and editing a nested child element by type

In the following example, the green rectangle is updated. It is accessed as the first child rectangle
of the second child `g` tag.


```{r}
doc        <- doc_orig$copy()
small_rect <- doc$child$g[[2]]$child$rect[[1]]

small_rect$update(fill = 'lightblue')
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```


# Finding any nested child element by attribute

In the following example, all elements with with green or light grey fill are found and updated


```{r}
doc      <- doc_orig$copy()
rg_elems <- doc$find(attribs = list(fill=c('lightgrey', 'green')))

purrr::walk(rg_elems, ~.x$update(fill = 'blue'))
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```


# Finding any nested child element by attribute and tag name.

In the following example, all rectangles with a black outline (stroke) are found and updated


```{r}
doc        <- doc_orig$copy()
rect_elems <- doc$find(tag = 'rect', attribs = list(stroke = 'black'))

purrr::walk(rect_elems, ~.x$update(fill = 'black', stroke = 'green'))
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r echo = FALSE}
if (interactive()) {
  doc$show()
} else {
  doc
}
```














