---
title: "editing-svgs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{editing-svgs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(minisvg)
```

# Editing an Existing SVG

It is possible for {minisvg} to pull in external SVG and edit it.

However, the capabilities are not very advanced.  This is mostly because my 
focus in writing {minisvg} was in **creating** SVG documents in R.

Since SVG documents are just XML documents, you can just use [xml2](https://github.com/r-lib/xml2) to 
manipulate the nodes.  However, this will require a conversion from {minisvg} to {xml2} using `xml2::read_xml(as.character(svg_doc))`.

This vignette will evolve as I add more SVG manipulation methods.  


# Basic editing.

A {minisvg} SVG document is just a tree of R6 objects, where each object represents
a single SVG tag (e.g. `<rect>` or `<pattern>`).  Each object has a list of children (`$childen`) and
a list of attributes (`$attrib`).

Once an external SVG is parsed into {minisvg} format, you can then directly manipulate the individual 
objects. 

In the following example, an SVG document containing a single rectangle is read into {minisvg}.  
The rectangle is identified, and its attributes are update to change the `fill` colour.



```{r}
library(minisvg)
foreign_svg <- '
<svg width="400" height="400" viewBox="0 0 400 400" xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink">
  <rect fill="black" x="10%" y="10%" width="80%" height="80%" />
</svg>'

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Parse the text as SVG into {minisvg} format. Underneath the hood, this
# actually uses `xml2::parse_xml()`
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
my_svg <- minisvg::parse_svg_doc(foreign_svg)

my_svg
```


```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Extract the first rectangle and change its fill attribute
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
first_rect <- my_svg$children[[1]]
first_rect$attribs$fill <- 'green'

my_svg
```

```{r echo=FALSE, comment=" "}
print(my_svg)
```


