---
title: "MathML-in-SVG"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MathML-in-SVG}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(minisvg)
```


# Introduction

Literal SVG and HTML strings can be included using the `SVGLiteral` R6 class.

This may be useful when:

* You have a character string containing SVG text from an external source to 
  include directly into your document.
* You have literal HTML that you'd like to include as a `<foreignObject>` within
  the SVG
* You have an object which can be coerced to a character string e.g. a 
[`minihtml`](https://github.com/coolbutuseless/minihtml) document
  

# MathML

[MathML](https://en.wikipedia.org/wiki/MathML) is an markup language for 
describing mathematical notation.

```{r}
mathml <- '
<math xmlns = "http://www.w3.org/1998/Math/MathML">
   <mrow>
      <mi>A</mi>
      <mo>=</mo>

      <mfenced open = "[" close="]">

         <mtable>
            <mtr>
               <mtd><mi>x</mi></mtd>
               <mtd><mi>y</mi></mtd>
            </mtr>

            <mtr>
               <mtd><mi>z</mi></mtd>
               <mtd><mi>w</mi></mtd>
            </mtr>
         </mtable>

      </mfenced>
   </mrow>
</math>'
```


# Inserting literal HTML into an SVG

* Create a `<foreignObject>` 
* Add an `SVGLiteral` node to the `<foreignObject>` 

```{r}

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create an SVG document with a grey rectangle
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- svg_doc()
doc$rect(x = "10%", y = "10%", width = "80%", height = "80%", fill = "silver")

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a literal node with the mathml
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
lit <- SVGLiteral$new(mathml)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Create a foreign object and add the literal object to it.
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
fo <- stag$foreignObject(x = 50, y = 50, width = 100, height = 100)
fo$append(lit)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# append the foreign object to the document
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc$append(fo)

doc
```

