---
title: "specifying-coords-for-polygons-and-polylines"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{specifying-coords-for-polygons-and-polylines}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(minisvg)
```


# Introduction

The SVG tags for `<polygon>` and `<polyline>` require a `points` argument which 
represents the coordinates of the vertices as a single string e.g. "0,0 0,1 1,1 1,0".

This is a little awkward to do from R, so the creation of polygons and polylines
have some alternate methods for specifying vertices.

# How to create a polygon or polyline

1. Using `stag`. E.g. `stag$polygon(...)`
2. Using `SVGElement$new('polygon', ...)`
3. Adding to an exisint element with `elem$add('polygon', ...)`


# Using `points`

The actual SVG `points` argument for `<polygon>` and `<polyline>` is a single
string of the form `x0,y0 x1,y1 x2,y2 ...`

```{r}
doc <- svg_doc(width=150, height=150)
doc$add('polygon', points = "0,0 100,0 100,100 0,100", fill = 'blue')
```


<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r}
doc
```


# Using `xs` and `ys` 

Can use `xs` and `ys` numeric vectors which contain the coordinates.

```{r}
xs <- c(0, 100, 100, 0)
ys <- c(0, 0, 100, 100)

doc <- svg_doc(width=150, height=150)
doc$add('polygon', xs = xs, ys = ys, fill = 'green')
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r}
doc
```

# Using `xs` as a data.frame

`xs` can be a data.frame with `x` and `y` numeric columns representing the coorindates.


```{r}
coords_df <- data.frame(
  x = c(0, 100, 100, 0),
  y = c(0, 0, 100, 100)
)

doc <- svg_doc(width=150, height=150)
doc$add('polygon', xs = coords_df, fill = 'pink')
```

<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r}
doc
```




# Using `xs` as a matrix

`xs` can be a matrix with the first 2 columns representing the coorindates.

```{r}
coords_mat <- matrix(c(
  0, 100, 100, 0,  
  0, 0, 100, 100),
  ncol = 2
)

doc <- svg_doc(width=150, height=150)
doc$add('polygon', xs = coords_df, fill = 'orange')
```


<details closed>
<summary> Show SVG text (click to open) </summary>
```{r echo=FALSE}
print(doc)
```
</details> <br />

```{r}
doc
```











