---
title: "Transformations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Transformations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>"
)
```

```{r setup}
library(minisvg)
```


## Introduction

This example was taken from the tutorial on attribute transforms on [MDN](https://developer.mozilla.org/en-US/docs/Web/SVG/Attribute/transform)

* The outline of the heart is defined as a `path`
* The path is shown as a red outline
* A copy of this path is filled with grey and transformed to mimic a shadow

```{r comment=''}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Define the heart shape
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
heart_shape <- stag$path(
  id="heart", 
  d="M 10,30 A 20,20 0,0,1 50,30 A 20,20 0,0,1 90,30 Q 90,60 50,90 Q 10,60 10,30 z"
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Style the heart shape to look like a shadow on the ground (using transforms)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
heart_shadow <- stag$g(
  fill = 'grey',
  svg_prop$transform$rotate(-10, 50, 100),
  svg_prop$transform$translate(-36, 45.5),
  svg_prop$transform$skewX(40),
  svg_prop$transform$scale(1, 0.5),
  heart_shape
)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Style the heart shape as an outline
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
heart_outline <- stag$use(href='#heart', fill = 'none', stroke = 'red')

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Build the SVG document with the shadow and outline
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
doc <- SVGDocument$new(
  width = 150, height = 100, viewBox = "-40 0 150 100",
  heart_shadow,
  heart_outline
)
```


<!-- Raw HTML output. hidden by default -->
<details closed>
<summary> <span title='Raw HTML'> Raw SVG Text (click to open) </span> </summary>
```{r echo = FALSE, comment=""}
print(doc)
```
</details><br />


```{r echo = FALSE}
doc
```



## Details

Unlike other attributes on SVG nodes, transformations are treated as cumulative.

For other attributes, setting a new value overwrites the old, but for transforms
they are concatenated.

To reset the transforms on an element, use `$reset_transform()`




